Towards human SuperEEG

### 2018-10-08 paper/boneyard.tex
JRM finished round of edits (still needs final coat of polish)

>>>>

% old discussion section

%DISCUSSION POINTS
%recap main approach
SuperEEG infers full-brain activity patterns by leveraging
correlations in those patterns of brain activity within and across people.  Although
the approach may, in principle, be used to infer brain activity
\textit{anywhere} in the brain, the inferences perform slightly better for
regions with dense electrode sampling across patients.  (Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
are included in the inference procedure, this suggests that reconstruction accuracy should improve.

%why does it work?  redundancy of brain
A fundamental assumption of the SuperEEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal18}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that SuperEEG relies on are
violated, how can the SuperEEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g., of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
SuperEEG approach that leverage resting state fMRI or structural data
[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g., informed
by structural MRI scans) may improve the predictive performance of the
approach.

%This technique relies on recordings from many patients performing the
%same basic cognitive task.  To what extent do these findings
%generalize across studies?  For example, could one combine recordings
%from several studies to improve our ability to reconstruct neural
%activity?
One potential limitation of the SuperEEG approach is that the above
assumption of covariance stability across people may be violated even
more if different patients are performing different cognitive tasks.
To understand of the extent to which the current findings generalize across
cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks. Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
matrix.  Or, using a more sophisticated approach, one could create a
hierarchical model whereby each task-specific covariance matrix was
modeled as a perturbation of a ``global'' task-unspecific covariance
matrix (which could in turn be informed by fMRI or DTI data).
% Alternatively, if the covariance matrix is stable across tasks, this would
% suggest that recordings from multiple studies could be combined to
% improve the overall reconstruction accuracy.

A second potential limitation of the SuperEEG approach is that it
does not provide a natural means of estimating the precise timing of
single-neuron action potentials.  Prior work has shown that gamma band
and broadband activity in the LFP may be used to estimate the firing
rates of neurons that underly the population contributing to the
LFP~\cite{MannEtal09}.  Because SuperEEG reconstructs LFPs throughout
the brain, one could in principle use gamma or broadband power in the
reconstructed signals to estimate the corresponding firing rates
(though not the timings of individual action potentials).

Beyond providing a means of estimating ongoing activity throughout the
brain using already implanted electrodes, our work also has
implications for where to place the electrodes in the first place.
Electrodes are typically implanted to maximize coverage of suspected
epileptogenic tissue.  However, our findings suggest that this approach
could be further optimized.  Specifically, one could leverage not only
the non-invasive recordings taken during an initial monitoring period
(as is currently done), but also recordings collected from other
patients.  We could then ask: given everything we know about the other
patients and from the scalp recordings of this new patient, where
should we place a fixed number of electrodes to maximize our ability
to map seizure foci?  As shown in Figure~\ref{fig:informap}, recordings
from different locations are differently informative in terms of
reconstructing the spatiotemporal patterns throughout the brain.
This property might be leveraged in decisions about where to
surgically implant electrodes in future patients.

%%%%

### 2018-10-08 paper/main.tex
JRM finished round of edits (still needs final coat of polish)

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods}
  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode
      locations.}  Each dot reflects the location of a single
    electrode implanted in the brain of a Dataset 1 patient.  A
    held-out recording location from one patient is indicated in red,
    and the patient's remaining electrodes are indicated in black.
    The electrodes from the remaining patients are colored by
    $k$-means cluster (computed using the full-brain correlation model
    shown in Panel D).  \textbf{B.~Radial basis function kernel.}
    Each electrode contributed by the patient (black) weights on the
    full set of locations under consideration (all dots in Panel A,
    defined as $\bar{R}$ in the text).  The weights fall off with
    positional distance (in MNI space) according to an RBF.
    \textbf{C.~Per-patient correlation matrices.}  After computing the
    pairwise correlations between the recordings from each patient's
    electrodes, we use RBF-weighted averages to estimate correlations
    between all locations in $\bar{R}$.  We obtain an estimated
    full-brain correlation matrix using each patient's
    data. \textbf{D.~Merged correlation model.}  We combine the
    per-patient correlation matrices (Panel C) to obtain a single
    full-brain correlation model that captures information contributed
    by every patient.  Here we have sorted the rows and columns to
    reflect $k$-means clustering labels~\citep[using
    $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their
    correlations with the rest of the brain (i.e., rows of the matrix
    displayed in the panel).  The boundaries denote the cluster
    groups.  The rows and columns of Panel C have been sorted using
    teh Panel D-derived cluster labels.  \textbf{E.~Reconstructing activity
      throughout the brain.}  Given the observed recordings from the
    given patient (shown in black; held-out recording is shown in
    blue), along with a full-brain correlation model (Panel D), we
    use Equation~\ref{eqn:reconstruction} to reconstruct the most
    probable activity at the held-out location (red).}
  \label{fig:methods}
\end{figure}

@@

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model derived from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from a single patient may be used to estimate held-out data.  This
allows us to ask how much information about the activity at a given
electrode might be inferred through (a) volume conductance or other
sources of ``leakage'' from activity patterns measured from the
patient's other electrodes and (b) across-electrode correlations
learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: XXX;
$t$-test comparing mean of distribution of $z$-transformed
per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
especially conservative test, given that the across-patient SuperEEG
reconstructions exclude (from the correlation matrix estimates) all
data from the patient whose data is being reconstructed.  We repeated
each of these analyses on a second independent datset and found
similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). We also
replicated this result separately for each of the two experiments from
Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding,
that when reconstructing held-out data from a given patient
correlation models derived from \textit{other} patient's data yield
higher reconstruction accuracy than correlation models derived from
that patient, has two important implications.  First, it implies that
distant electrodes provide additional predictive power to the data
reconstructions beynd the information contained solely in nearby
electrodes.  (This follows from the fact that each patient's
electrodes are implanted in a unique set of locations, so for any
given electrode the closest electrodes in the full dataset are likely
to come from the same patient.)  Second, it implies that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across people.

@@

The recordings we analyzed from Dataset 1 comprised data collected as
the patients performed a variety of (essentially uncontrolled) tasks
throughout each day's recording session.  That we observed reliable
reconstruction accuracy across patients suggests that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across tasks.  We tested this finding more explicitly using
Dataset 2.  In Dataset 2, the recordings were limited to times when
each patient was participating in each of two experiments (Experiment
1, a random-word list free recall task, and Experiment 2, a
categorized list free recall task).  We wondered whether a correlation
model trained using data only from one experiment might yield good
predictions for data from the other experiment.  Further, we wondered
about the extent to which it might be benefitial or harmful to combine
data across tasks.

@@

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}B, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes contained
within a 20 MNI unit radius sphere centered on that voxel.  We defined
the \textit{density} at that location as this proportion.  Across
Datasets 1 and 2, the electrode placement densities were similar
(correlation by voxel: $r = 0.57, p < 10^{-10}$).  We wondered whether
regions with good covererage might be associated with better
reconstruction accuracy (e.g. Fig.~\ref{fig:corrmap}B, D indicate that
many electrodes in the MTL have relatively high reconstruction
accuracy, and occiptal electrodes tend to have relatively low
reconstruction accuracy).  To test whether this held more generally
across the entire brain, for each dataset we computed the electrode
placement density for each electrode from each patient (using the
proportion of \textit{other} patients' electrodes within 20 MNI units
of the given electrode).  We then correlated these density values with
the across-patient reconstruction accuracies for each electrode.
Contrary to our expectation, rather than positive correlations, we
found weak (but reliable) negative correlations between reconstruction
accuracy and density for both datasets (Dataset 1: $r = XXX, p = XXX$;
Dataset 2: $r = -0.16, p < 10^{-10}$).  This indicates that the
reconstruction accuracies we observed are not driven solely by
sampling density, but rather may also reflect higher order properties
of neural dynamics such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@

\textbf{JRM STOPPED HERE}

\section*{Discussion}
%DISCUSSION POINTS
%recap main approach
SuperEEG infers full-brain activity patterns by leveraging
correlations in those patterns of brain activity within and across people.  Although
the approach may, in principle, be used to infer brain activity
\textit{anywhere} in the brain, the inferences perform slightly better for
regions with dense electrode sampling across patients.  (Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
are included in the inference procedure, this suggests that reconstruction accuracy should improve.

%why does it work?  redundancy of brain
A fundamental assumption of the SuperEEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal18}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that SuperEEG relies on are
violated, how can the SuperEEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g., of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
SuperEEG approach that leverage resting state fMRI or structural data
[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g., informed
by structural MRI scans) may improve the predictive performance of the
approach.

%This technique relies on recordings from many patients performing the
%same basic cognitive task.  To what extent do these findings
%generalize across studies?  For example, could one combine recordings
%from several studies to improve our ability to reconstruct neural
%activity?
One potential limitation of the SuperEEG approach is that the above
assumption of covariance stability across people may be violated even
more if different patients are performing different cognitive tasks.
To understand of the extent to which the current findings generalize across
cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks. Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
matrix.  Or, using a more sophisticated approach, one could create a
hierarchical model whereby each task-specific covariance matrix was
modeled as a perturbation of a ``global'' task-unspecific covariance
matrix (which could in turn be informed by fMRI or DTI data).
% Alternatively, if the covariance matrix is stable across tasks, this would
% suggest that recordings from multiple studies could be combined to
% improve the overall reconstruction accuracy.

A second potential limitation of the SuperEEG approach is that it
does not provide a natural means of estimating the precise timing of
single-neuron action potentials.  Prior work has shown that gamma band
and broadband activity in the LFP may be used to estimate the firing
rates of neurons that underly the population contributing to the
LFP~\cite{MannEtal09}.  Because SuperEEG reconstructs LFPs throughout
the brain, one could in principle use gamma or broadband power in the
reconstructed signals to estimate the corresponding firing rates
(though not the timings of individual action potentials).

Beyond providing a means of estimating ongoing activity throughout the
brain using already implanted electrodes, our work also has
implications for where to place the electrodes in the first place.
Electrodes are typically implanted to maximize coverage of suspected
epileptogenic tissue.  However, our findings suggest that this approach
could be further optimized.  Specifically, one could leverage not only
the non-invasive recordings taken during an initial monitoring period
(as is currently done), but also recordings collected from other
patients.  We could then ask: given everything we know about the other
patients and from the scalp recordings of this new patient, where
should we place a fixed number of electrodes to maximize our ability
to map seizure foci?  As shown in Figure~\ref{fig:informap}, recordings
from different locations are differently informative in terms of
reconstructing the spatiotemporal patterns throughout the brain.
This property might be leveraged in decisions about where to
surgically implant electrodes in future patients.

@@

\section*{Code availability}
We have released an open-source SuperEEG Python toolbox.  All of the code used in this manuscript is on GitHub, and the code may be shared using a GitHub account accessible to the reviewers upon request.

\section*{Data availability}
The dataset analyzed in this study was generously shared by Michael J. Kahana.  A portion of the dataset may be downloaded \href{http://memory.psych.upenn.edu/Request_EEG_access?paper=SedeEtal03}{\underline{here}}.
\section*{Acknowledgements}
We are grateful for useful discussions with Luke J. Chang and Matthijs van der Meer.  We are also grateful to Michael J. Kahana for generously sharing
the ECoG dataset we analyzed in our paper, which was collected under
NIMH grant MH55687 to MJK.  Our work was also supported in part by NSF EPSCoR Award Number 1632738.  The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
\section*{Author Contributions}
J.R.M conceived and initiated the project. L.L.W.O. and A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the manuscript.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods}
  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode
      locations.}  Each dot reflects the location of a single
    electrode implanted in the brain of a Dataset 1 patient.  A
    held-out recording location from one patient is indicated in red,
    and the patient's remaining electrodes are indicated in black.
    The electrodes from the remaining patients are colored by
    $k$-means cluster (computed using the full-brain correlation model
    shown in Panel D).  \textbf{B.~Radial basis function kernel.}
    Each electrode contributed by the patient (black) weights on the
    full set of locations under consideration (all dots in Panel A,
    defined as $\bar{R}$ in the text).  The weights fall off with
    positional distance (in MNI space) according to an RBF.
    \textbf{C.~Per-patient correlation matrices.}  After computing the
    pairwise correlations between the recordings from each patient's
    electrodes, we use RBF-weighted averages to estimate correlations
    between all locations in $\bar{R}$.  We obtain an estimated
    full-brain correlation matrix using each patient's
    data. \textbf{D.~Merged correlation model.}  We combine the
    per-patient correlation matrices (Panel C) to obtain a single
    full-brain correlation model that captures information contributed
    by every patient.  Here we have sorted the rows and columns to
    reflect $k$-means clustering labels~\citep[using
    $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their
    correlations with the rest of the brain (i.e., rows of the matrix
    displayed in the panel).  The boundaries denote the cluster
    groups.  The rows and columns of Panel C have been sorted using
    the Panel D-derived cluster labels.  \textbf{E.~Reconstructing activity
      throughout the brain.}  Given the observed recordings from the
    given patient (shown in black; held-out recording is shown in
    blue), along with a full-brain correlation model (Panel D), we
    use Equation~\ref{eqn:reconstruction} to reconstruct the most
    probable activity at the held-out location (red).}
  \label{fig:methods}
\end{figure}

@@

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model derived from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from a single patient may be used to estimate held-out data.  This
allows us to ask how much information about the activity at a given
electrode might be inferred through (a) volume conductance or other
sources of ``leakage'' from activity patterns measured from the
patient's other electrodes and (b) across-electrode correlations
learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: XXX;
$t$-test comparing mean of distribution of $z$-transformed
per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
especially conservative test, given that the across-patient SuperEEG
reconstructions exclude (from the correlation matrix estimates) all
data from the patient whose data is being reconstructed.  We repeated
each of these analyses on a second independent dataset and found
similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). We also
replicated this result separately for each of the two experiments from
Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding,
that when reconstructing held-out data from a given patient
correlation models derived from \textit{other} patient's data yield
higher reconstruction accuracy than correlation models derived from
that patient, has two important implications.  First, it implies that
distant electrodes provide additional predictive power to the data
reconstructions beyond the information contained solely in nearby
electrodes.  (This follows from the fact that each patient's
electrodes are implanted in a unique set of locations, so for any
given electrode the closest electrodes in the full dataset are likely
to come from the same patient.)  Second, it implies that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across people.

@@

The recordings we analyzed from Dataset 1 comprised data collected as
the patients performed a variety of (essentially uncontrolled) tasks
throughout each day's recording session.  That we observed reliable
reconstruction accuracy across patients suggests that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across tasks.  We tested this finding more explicitly using
Dataset 2.  In Dataset 2, the recordings were limited to times when
each patient was participating in each of two experiments (Experiment
1, a random-word list free recall task, and Experiment 2, a
categorized list free recall task).  We wondered whether a correlation
model trained using data only from one experiment might yield good
predictions for data from the other experiment.  Further, we wondered
about the extent to which it might be beneficial or harmful to combine
data across tasks.

@@

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}B, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes contained
within a 20 MNI unit radius sphere centered on that voxel.  We defined
the \textit{density} at that location as this proportion.  Across
Datasets 1 and 2, the electrode placement densities were similar
(correlation by voxel: $r = 0.57, p < 10^{-10}$).  We wondered whether
regions with good covererage might be associated with better
reconstruction accuracy (e.g. Fig.~\ref{fig:corrmap}B, D indicate that
many electrodes in the MTL have relatively high reconstruction
accuracy, and occipital electrodes tend to have relatively low
reconstruction accuracy).  To test whether this held more generally
across the entire brain, for each dataset we computed the electrode
placement density for each electrode from each patient (using the
proportion of \textit{other} patients' electrodes within 20 MNI units
of the given electrode).  We then correlated these density values with
the across-patient reconstruction accuracies for each electrode.
Contrary to our expectation, rather than positive correlations, we
found weak (but reliable) negative correlations between reconstruction
accuracy and density for both datasets (Dataset 1: $r = XXX, p = XXX$;
Dataset 2: $r = -0.16, p < 10^{-10}$).  This indicates that the
reconstruction accuracies we observed are not driven solely by
sampling density, but rather may also reflect higher order properties
of neural dynamics such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@

\section*{Discussion}
Are our brain's networks static or dynamic?  And to what extent are
the network properties of our brains stable across people and tasks?
One body of work suggests that our brain's \textit{functional}
networks are dynamic~\citep[e.g., ][]{MannEtal18},
person-specific~\citep[e.g., ][]{FinnEtal15}, and
task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the
gross anatomical structure of our brains changes meaningfully over the
course of years as our brains develop, on the timescales of typical
neuroimaging experiments (i.e., hours to days) our anatomical networks
are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many
aspects of brain anatomy, including white matter structure, is largely
preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13,
  MoriEtal08} There are several possible means of reconciling this
apparent inconsistency between dynamic person- and task-specific
functional networks versus stable anatomical networks.  For example,
relatively small magnitude anatomical differences across people may be
reflected in reliable functional connectivity differences.  Along
these lines, one recent study found that diffusion tensor imaging
(DTI) structural data is similar across people, but may be used to
predict person-specific resting state functional connectivity
data~\citep{BeckEtal18}.  Similarly, other work indicates that
task-specific functional connectivity may be predicted by resting
state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.  Another
(potentially complementary) possibility is that our functional
networks are constrained by anatomy, but nevertheless exhibit
(potentially rapid) task-dependent changes~\citep[e.g.,
][]{SporBetz16}.

Here we have taken a model-based approach to studying whether high
spatiotemporal resolution activity patterns throughout the human brain
may be explained by a static connectome model that is shared across
people and tasks.  Specifically, we trained a model to take in
recordings from a subset of brain locations, and then predicted
activity patterns during the same interval, but at \textit{other}
locations that were held out from the model.  Our model, based on
Gaussian process regression, was built on three general hypotheses
about the nature of the correlational structure of neural activity
(each of which we tested).  First, we hypothesized that functional
correlations are stable over time and across tasks.  We found that,
although aspects of the patients' functional correlations that were
stable across tasks, we achieved better reconstruction accuracy when
we trained the model on within-task data~\citep[we acknowledge that
our general approach could potentially be extended to better model
across-task changes, following][and others]{ColeEtal16, TavoEtal16}.
Second, we hypothesized that some of the correlational structure of
people's brain activity is similar across individuals.  Consistent
with this hypothesis, our model explained the data best when we
trained the correlation model using data from \textit{other}
patients-- even when compared to a correlation model trained using the
same patient's data.  Third, we resolved ambiguities in the data by
hypothesizing that neural activity from nearby sources will tend to be
similar, all else being equal.  This hypothesis was supported through
our finding that all of the models we trained that incorporated this
spatial smoothness assumption predicted held-out data well above chance.

One potential limitation of our approach is that it does not provide a
natural means of estimating the precise timing of single-neuron action
potentials.  Prior work has shown that gamma band and broadband
activity in the LFP may be used to estimate the firing rates of
neurons that underly the population contributing to the
LFP~\cite{MillEtal08, MannEtal09, JacoEtal10, CronEtal11}.  Because
SuperEEG reconstructs LFPs throughout the brain, one could in
principle use gamma or broadband power in the reconstructed signals to
estimate the corresponding firing rates (though not the timings of
individual action potentials).

Beyond providing a means of estimating ongoing activity throughout the
brain using already implanted electrodes, our work also has
implications for where to place the electrodes in the first place.
Electrodes are typically implanted to maximize coverage of suspected
epileptogenic tissue.  However, our findings suggest that this approach
could be further optimized.  Specifically, one could leverage not only
the non-invasive recordings taken during an initial monitoring period
(as is currently done routinely), but also recordings collected from other
patients.  We could then ask: given everything we know about the other
patients and from the scalp recordings of this new patient, where
should we place a fixed number of electrodes to maximize our ability
to map seizure foci?  As shown in Figure~\ref{fig:informap}, recordings
from different locations are differently informative in terms of
reconstructing the spatiotemporal patterns throughout the brain.
This property might be leveraged in decisions about where to
surgically implant electrodes in future patients.

@@

\section*{Code availability}
We have published an open-source toolbox implementing the SuperEEG
algorithm.  It may be downloaded \href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}.

\section*{Data availability}
The dataset analyzed in this study was generously shared by Michael Kahana.  A portion of Dataset 1 may be downloaded
\href{http://memory.psych.upenn.edu/Request_EEG_access?paper=SedeEtal03}{\underline{here}}.
Dataset 2 may be downloaded
\href{http://memory.psych.upenn.edu/Request_EEG_access?paper=EzzyEtal17}{\underline{here}}.

\section*{Acknowledgements}
We are grateful for useful discussions with Luke J. Chang, Uri Hasson,
Josh Jacobs, Michael Kahana, and Matthijs van der Meer.  We are also
grateful to Michael Kahana for generously sharing the ECoG data we
analyzed in our paper, which was collected under NIMH grant MH55687
and DARPA RAM Cooperative Agreement N66001-14-2-4-032, both to MJK.
Our work was also supported in part by NSF EPSCoR Award Number 1632738
and by a sub-award of DARPA RAM Cooperative Agreement
N66001-14-2-4-032 to JRM.  The content is solely the responsibility of
the authors and does not necessarily represent the official views of
our supporting organizations.

\section*{Author Contributions}
J.R.M conceived and initiated the project. L.L.W.O. and A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the manuscript.
